Data Management for LSST Special Programs

### 2023-10-19 sec_proc.tex
org updates

\section{Processing Data from Special Programs}\label{sec:proc}

@@

\textbf{How WFD and Special Program data would co-exist.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the WFD program as 
described in Section 3 of the DPDD \citedsp{lse-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.

Including visits from Special Programs in regular Prompt processing alongside
vists from the WFD program is not, in general, anticipated to affect WFD science goals.
For example, analyses for a WFD-only subset could still be done using the program and
region labels described in Section~\ref{ssec:sci_labels}, which would be
propogated to difference images, difference-image catalogss, and alerts.

\textbf{Potential issues with Prompt processing for untiled sequences from Special Programs.}
There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images: images at the same pointing or which overlap.
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.

@@

\item \textbf{DIA Object histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
WFD program fields. 
The Prompt pipeline resources are also sized for the
WFD program, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribtuion,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.

@@

>>>>

\section{Details and Challenges of Processing Data from Special Programs}\label{sec:proc}

@@

\textbf{How WFD and Special Program data would co-exist.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the WFD program as 
described in Section 3 of the DPDD \citedsp{lse-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.
Including visits from Special Programs in regular Prompt processing alongside
vists from the WFD program is not, in general, anticipated to affect WFD science goals.
For example, analyses for a WFD-only subset could still be done using the program and
region labels described in Section~\ref{ssec:sci_labels}, which would be
propogated to difference images, difference-image catalogss, and alerts.

\textbf{Potential issues with Prompt processing for untiled sequences from Special Programs.}
There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images (images at the same pointing or which overlap).
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.

@@

\item \textbf{DIA Object histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
WFD program fields. 
The Prompt pipeline resources are also sized for the
WFD program, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribtuion,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.
Alerts from Special Programs data are subject to the same latency
requirements as WFD program alerts (Section~\ref{ssec:req_proc}).

@@

\subsubsection{Scenarios to illustrate ``possible and necessary"}
